Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-15 paper.tex
add explanation on uncertainty

@@

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition. While it has demonstrated the
capability to measure the uncertainty on output fuel cycle metrics and relative
contributions, it has only been applied to systematic uncertainties per
facilities (parameters randomly generated at each new facility deployment).
This kind of study will to be extended to random uncertainty (new parameter
values at each occurrence) and completely systematic uncertainty (shared by all the
facilities of a kind).

>>>>

The uncertainty on the different parameters have been considered for this study
as systematic for each new deployed facilities: each time a new facility is
deployed (such as a reactor or a fuel fabrication facility) a new set a
parameter is computed.

@@

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition. While it has demonstrated the
capability to measure the uncertainty on output fuel cycle metrics and their
relative contributions, it has only been applied to systematic uncertainties per
facilities (parameters randomly generated at each new facility deployment).
This kind of study will to be extended to random uncertainty (new parameter
values at each occurrence) and completely systematic uncertainty (shared by all
the facilities of a kind).
